\mythesistitleNOTSYNPOSIS

### 2012-02-27 src/030chap3.tex
proof read TILL Sec 3.2.2

Section~\ref{sec:myresearchintro} recalls the idea of tree path
labeling. The necessary preliminaries with definitions etc. are
presented in Section~\ref{ch:prelims}. Section~\ref{sec:feasible}
documents a characterization for feasible path labelings. In
Section~\ref{sec:wallacesol} we demonstrate the algorithm described in
Section~\ref{sec:feasible} by working out the solution to an example.
Section~\ref{sec:spltargettree} describes two special cases where the
target tree is of a particular family of trees. The first one is shown
to be equivalent to COP testing in
Section~\ref{sec:icpplicpia}. Section~\ref{sec:ksubdivstar} discusses
the second special case and presents a polynomial time algorithm to
find the tree path labeling of a given set system from a given
\kstar. Section~\ref{sec:norestraint} discusses the plain vanilla
version where the target tree has no restrictions and the algorithm to
find a feasible TPL, if any, in this case.  Finally, in Section
\ref{sec:tplcomplexity} we discuss the complexity of the algorithms
seen thus far and we conclude by showing that \cop testing, which is a
special case of \TPL, is in \logspace.

\section[Summary of problems]{Summary of Proposed Problems}
\label{sec:myresearchintro}
In Section~\ref{sec:motive} we see that consecutive-ones property and
its equivalent problem of interval labeling of a hypergraph is a
special case of the general problem of tree path labeling of path
hypergraphs. Moreover, Section~\ref{sec:icpiasurvey} describes how the
problem of consecutive-ones property testing can be easily seen as a
simple constraint satisfaction problem involving a hypergraph or a
system of sets from a universe. Every column (row) of the binary
matrix can be converted into a set of non-negative integers which are
the indices of the rows (columns) with {\un}s in that column
(row). When observed in this context, if the matrix has the COP on
columns (rows), a reordering of its rows (columns) will result in sets
that have only consecutive integers. In other words, the sets after
applying the COP row (column) permutation are intervals.  In this
form, one can see that this is indeed the problem of finding interval
assignments to the given set system with a single permutation of the
universe (set of row or column indices for COP of columns or rows,
respectively) which permutes each set to an interval. The result in
\cite{nsnrs09} (see Theorems~\ref{th:icpia2} and \ref{th:icpia1})
characterizes interval assignments to the sets which can be obtained
from a single permutation of the universe. The cardinality of the
interval assigned to it must be same as the cardinality of the set,
and the intersection cardinality of any two sets must be same as the
intersection cardinality of the corresponding intervals. This is a
necessary and sufficient condition.

@@

With respect to computing a feasible TPL, as suggested by \CFTPL
problem, we were unable to discover an efficient algorithm for
it. However, we consider two special cases of the same on special
target trees -- namely, \CFTPLINT and \CFTPLKTREE on intervals and
\kstars, respectively.  Section~\ref{sec:spltargettree} discusses
these problems and their polynomial time solutions.  \CFTPLINT is a
demonstrated to be the known problem of \COP testing. The polynomial
time solution to \CFTPLKTREE is a new result by us.

@@

An algorithm for \CFTPL on general trees which is less efficient than
polynomial time is presented in
Section~\ref{sec:norestraint}.

>>>>

Section~\ref{sec:myresearchintro} recalls the idea of tree path
labeling. The necessary preliminaries with definitions etc. are
presented in Section~\ref{ch:prelims}. Section~\ref{sec:feasible}
documents a characterization for feasible path labelings. In
Section~\ref{sec:wallacesol} we demonstrate the algorithm described in
Section~\ref{sec:feasible} by working out the solution to an example.
Section~\ref{sec:spltargettree} describes two special cases where the
target tree is of a particular family of trees. The first one is shown
to be equivalent to COP testing in
Section~\ref{sec:icpplicpia}. Section~\ref{sec:ksubdivstar} discusses
the second special case and presents a polynomial time algorithm to
find the tree path labeling of a given set system from a given
\kstar. Section~\ref{sec:norestraint} discusses the plain vanilla
version where the target tree has no restrictions and the algorithm to
find a feasible TPL, if any, in this case.  Finally, in Section
\ref{sec:tplcomplexity} we discuss the complexity of \TPL
and we conclude by showing that \cop testing, which is a
special case of \TPL, is in \logspace.

\section[Summary of problems]{Summary of Proposed Problems}
\label{sec:myresearchintro}
In Section~\ref{sec:motive} we see that consecutive-ones property and
its equivalent problem of interval labeling of a hypergraph is a
special case of the general problem of tree path labeling of path
hypergraphs. Moreover, Section~\ref{sec:icpiasurvey} describes how the
problem of consecutive-ones property testing can be easily seen as a
simple constraint satisfaction problem involving a hypergraph or a
system of sets from a universe. Every column (row) of the binary
matrix can be converted into a set of non-negative integers which are
the indices of the rows (columns) with {\un}s in that column
(row). When observed in this context, if the matrix has the COP on
columns (rows), a reordering of its rows (columns) will result in sets
that have only consecutive integers. In other words, the sets after
applying the COP row (column) permutation are intervals.  In this
form, one can see that this is indeed the problem of finding interval
assignments to the given set system with a single permutation of the
universe (set of row or column indices for COP of columns or rows,
respectively) which permutes each set to an interval. The result in
\cite{nsnrs09} (see Theorems~\ref{th:icpia1} and \ref{th:icpia2})
characterizes interval assignments to the sets which can be obtained
from a single permutation of the universe. The cardinality of the
interval assigned to it must be same as the cardinality of the set,
and the intersection cardinality of any two sets must be same as the
intersection cardinality of the corresponding intervals. This is a
necessary and sufficient condition.

@@

With respect to computing a feasible TPL, as suggested by \CFTPL
problem, we were unable to discover an efficient algorithm for
it. However, we consider two special cases of the same on special
target trees -- namely, \CFTPLINT and \CFTPLKTREE on intervals and
\kstars, respectively.  Section~\ref{sec:spltargettree} discusses
these problems and their polynomial time solutions.  \CFTPLINT is the
known problem of \COP testing. The polynomial time solution to
\CFTPLKTREE is a new result by us.

@@

An algorithm for \CFTPL on arbitrary trees is presented in
Section~\ref{sec:norestraint} which would run in polynomial time if
two subproblems we identify are polynomial time solvable.
